Quality Definitions of Qualities

### 2019-11-06 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Addition of owner information to each quality
Added explicit Proposed Definition to each quality.

Purpose and scope of the document.  \wss{Needs to be filled in.  Should
  reference the overal research proposal, and the ``state of the practice''
  exercise in particular.}

@@

\subsection{Installability}
\begin{itemize}
\item{Definition 1:} A measure of the ease of installation.
\item{Definition 2:} Installability is related to the amount of human effort
  required to install a software in a designated environment
  \cite{berander2005software}.
\item{Definition 3:} ``The capability of a software product to be installed in a
  specified environment'' \cite{berander2005software}.
\item{Definition 4:} ``The efficacy of the installation, uninstallation or
  reinstallation process of a software product in a specified enviroment''
  (\cite{iso201017043})
\item {\textbf{Proposed definition}:} (Definition 2)
\end{itemize}

\subsection{Correctness}

@@

\noindent \textbf{Proposed definition}: Definition~\ref{CorrectDefnSelected}

@@

\subsection{Verifiability}

@@

@@

\subsection{Validatability}

@@

\subsection{Reliability}

@@

\subsection{Robustness}
\begin{defn}
  The degree to which a system or component can function correctly in the
  presence of invalid inputs or stressful environmental conditions
  \citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
  The quality can be further informally refined as the ability of a software to
  keep an acceptable behavior, expressed in terms of robustness requirements, in
  spite of exceptional or unforeseen execution conditions (such as the
  unavailability of system resources, communication failures, invalid or
  stressful inputs, etc.) \citep{fernandez2005model}.
\end{defn}
\begin{defn}
  Code possesses the characteristic of robustness to the extent that it can
  continue to perform despite some violation of the assumptions in its
  specification \citep{boehm2007software}.
\end{defn}
\begin{defn} \label{RobustnessDefnSelected}
  A program is robust if it behaves "reasonably", even in circumstances that
  were not anticipated in the requirements specification - for example, when it
  encounters incorrect input data or some hardware malfunction
  \citep{ghezzi1991fundamentals}.
\end{defn}

\noindent \textbf{Chosen definition:} Definition \ref{RobustnessDefnSelected} rephrased:

@@

\subsection{Performance}
\begin{defn}
The degree to which a system or component accomplishes its designated functions
within given constraints, such as speed, accuracy, or memory usage
\citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn} \label{PerformanceDefnSelected}
How well or how rapidly the system must perform specific functions. Performance
requirements encompass speed (database response times, for instance), throughput
( transactions per second), capacity (con-current usage loads), and timing (hard
real-time demands) \citep{wiegers2003softreq}.
\end{defn}
\begin{defn}
In software engineering we often equate performance with efficiency. A software
system is efficient if it uses computing resources economically
\citep{ghezzi1991fundamentals}.
\end{defn}

\noindent \textbf{Chosen definition:} Definition \ref{PerformanceDefnSelected}:

@@

\subsection{Usability}

@@

\subsection{Maintainability}

@@

\noindent \textbf{Chosen definition:} Combined Definition
\ref{MaintainabilityDefnSelected1} and Definition
\ref{MaintainabilityDefnSelected2}:

@@

\subsection{Reusability}
\begin{defn} 
The degree to which a software module or other work product can be used in more
than one software system \citep{IEEEStdGlossarySET1990}. 
\end{defn}
\begin{defn}
Extent to which a program [or parts of a program] can be reused in other
applications - related to the packaging and scope of the functions that the
program performs \citep{pressman2005software}.
\end{defn}
\begin{defn} \label{ReusabilityDefnSelected}
The extent to which a software component can be used with or without adaptation
in a problem solution other than the one for which it was originally developed
\citep{kalagiakos2003non}.
\end{defn}
\begin{defn}
Reusability is the likelihood a segment of source code that can be used again to
add new functionalities with slight or no modification \citep{sandhu2010survey}.
\end{defn}

\noindent \textbf{Chosen definition:} Definition \ref{ReusabilityDefnSelected}:

@@

\subsection{Portability}
\begin{defn}
The ease with which a system or component can be transferred from one hardware
or software environment to another \citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
An application is portable across a class of environments to the degree that the
effort required to transport and adapt it to a new environment in the class is
less than the effort of redevelopment \citep{mooney1990strategies}.
\end{defn}
\begin{defn} \label{PortabilityDefnSelected}
Effort required to transfer the program from one hardware and/or software system
environment to another \citep{pressman2005software}.
\end{defn}
\begin{defn}
A set of attributes that bear on the ability of software to be transferred from
one environment to another (including the organizational, hardware, of software
environment)\citep{pfleeger2006software}.
\end{defn}
\begin{defn}
Code possesses the characteristic of portability to the extent that it can be
operated easily and well on computer configurations other than its current
one. This implies that special function features, not easily available at other
facilities, are not used, that standard library functions and subroutines are
selected for universal applicability, and so on \citep{boehm2007software}.
\end{defn}
\begin{defn}
Portability refers to the ability to run a system on different hardware
platforms \citep{ghezzi1991fundamentals}.
\end{defn}

\noindent \textbf{Chosen definition:} Definition \ref{PortabilityDefnSelected}
rephrased:

@@

\subsection{Understandability}

@@

\subsection{Interoperability}

\noindent \textbf{Chosen definition:} Def \ref{InteroperabilitySelected}
rephrased: Interoperability is the ability of different information systems,
devices and applications (‘systems’) to access, exchange, integrate and
cooperatively use data in a coordinated manner, within and across
organizational, regional and national boundaries, to provide timely and seamless
portability of information.

@@

\subsection{Visibility/Transparency}
\noindent \textbf{Chosen definition:} Def \ref{VisibilitySelected}.

@@

\subsection{Reproducibility}

@@

\subsection{Productivity}

\noindent \textbf{Chosen definition:} The first sentence of Def
\ref{ProductivitySelected}: Productivity is the amount of output (what is
produced) per unit of input used.
\begin{defn}
The best definition of the productivity of a process is
\[\text{Productivity} = \dfrac{\text{Outputs produced by the
process}}{\text{Inputs consumed by the process}}\]
Defining inputs. For the software process, providing a meaningful definition of
inputs is a nontrivial but generally workable problem. Inputs to the software
process generally comprise labor, computers, supplies, and other support
facilities and equipment. Defining outputs. The big problem in defining software
productivity is defining outputs. Here we find a defining delivered source
instructions (DSI) or lines of code as the output of the software process is
totally inadequate, and they argue that there are a number of deficiencies in
using DSI. However, most organizations doing practical productivity measurement
still use DSI as their primary metric \citep{Boehm1987}.
\end{defn}
\begin{defn}
\label{ProductivitySelected}
Productivity is the amount of output (what is produced) per unit of input
used.If we can measure the size of the software product and the effort required
to develop the product, we have:
\begin{align}
\text{productivity} = \text{size}/\text{effort}
\end{align}
Equation (1) assumes that size is the output of the software production process
and effort is the input to the process. This can be contrasted with the
viewpoint of software cost models where we use size as an independent variable
(i.e., an input) to predict effort which is treated as an output. Equation (1)
is simple to operationalize if we have a single dominant size measure, for
example, product size measured in lines of code \citep{Kitchenham2004}.
\end{defn}

\subsection{Sustainability}

@@

@@

\subsection{Completeness}

\noindent \textbf{Chosen definition:} The first sentence of Def
\ref{CompletenessSelected}: A specification is complete to the extent that all
of its parts are present and each part is fully developed.

@@

\ad{The following part was here before my modification}

Documentation is said to be complete when all the requirements of the software
are detailed. That is, each goal, functionality, attribute, design constraint,
value, data, model, symbol, term (with its unit of measurement if applicable),
abbreviation, acronym, assumption and performance requirement of the software is
defined. The software's response to all classes of inputs, both valid and
invalid and for both desired and undesired events, also needs to be specified.

\subsection{Consistency}

\noindent \textbf{Chosen definition:} Def \ref{ConsistencySelected}.

@@

\ad{The following part was here before my modification}

Documentation is said to be consistent when no subset of individual statements
are in conflict with each other. That is, a specification of an item made at one
place in the document should not contradict the specification of the same item
at another location.

\subsection{Modifiability}

@@

\subsection{Traceability}

@@

\subsection{Unambiguity}

@@

\subsection{Verifiability}

@@

\subsection{Abstract}

>>>>

Purpose and scope of the document.  \wss{Needs to be filled in.  Should
  reference the overall research proposal, and the ``state of the practice''
  exercise in particular.}

@@

\subsection{Installability \oo{owner}}

\begin{defn}
  A measure of the ease of installation.  \wss{Where does this definition come
    from? Please add a citation.}
\end{defn}

\begin{defn} \label{DefnInstallability}
  Installability is related to the amount of human effort required to install a
  software in a designated environment \cite{berander2005software}.
\end{defn}

\begin{defn}
  ``The capability of a software product to be installed in a specified
  environment'' \cite{berander2005software}.
\end{defn}

\begin{defn}
  ``The efficacy of the installation, uninstallation or reinstallation process
  of a software product in a specified environment'' (\cite{iso201017043})
\end{defn}

\noindent \textbf{Proposed Definition}

Definition~\ref{DefnInstallability}.

\wss{The rationale is missing.  Please add.}

\subsection{Correctness \oo{owner}}

@@

\noindent \textbf{Proposed Definition}

Definition~\ref{CorrectDefnSelected}

\noindent \textbf{Reasoning}

@@

\subsection{Verifiability \oo{owner}}

@@

\noindent \textbf{Proposed Definition}

@@

\subsection{Validatability \oo{owner}}

@@

\subsection{Reliability \oo{owner}}

@@

\subsection{Robustness \pmi{owner}}
\begin{defn}
  The degree to which a system or component can function correctly in the
  presence of invalid inputs or stressful environmental conditions
  \citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
  The quality can be further informally refined as the ability of a software to
  keep an acceptable behavior, expressed in terms of robustness requirements, in
  spite of exceptional or unforeseen execution conditions (such as the
  unavailability of system resources, communication failures, invalid or
  stressful inputs, etc.) \citep{fernandez2005model}.
\end{defn}
\begin{defn}
  Code possesses the characteristic of robustness to the extent that it can
  continue to perform despite some violation of the assumptions in its
  specification \citep{boehm2007software}.
\end{defn}
\begin{defn} \label{RobustnessDefnSelected}
  A program is robust if it behaves "reasonably", even in circumstances that
  were not anticipated in the requirements specification - for example, when it
  encounters incorrect input data or some hardware malfunction
  \citep{ghezzi1991fundamentals}.
\end{defn}

\noindent \textbf{Proposed Definition}

Definition \ref{RobustnessDefnSelected} rephrased:

@@

\subsection{Performance \pmi{owner}}

\begin{defn}
The degree to which a system or component accomplishes its designated functions
within given constraints, such as speed, accuracy, or memory usage
\citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn} \label{PerformanceDefnSelected}
How well or how rapidly the system must perform specific functions. Performance
requirements encompass speed (database response times, for instance), throughput
( transactions per second), capacity (con-current usage loads), and timing (hard
real-time demands) \citep{wiegers2003softreq}.
\end{defn}
\begin{defn}
In software engineering we often equate performance with efficiency. A software
system is efficient if it uses computing resources economically
\citep{ghezzi1991fundamentals}.
\end{defn}

\noindent \textbf{Proposed Definition}

Definition \ref{PerformanceDefnSelected}:

@@

\subsection{Usability \jc{owner}}

@@

\noindent \textbf{Proposed Definition}

\wss{Still needs to be completed}

\subsection{Maintainability \pmi{owner}}

@@

\noindent \textbf{Proposed Definition}

Combined Definition
\ref{MaintainabilityDefnSelected1} and Definition
\ref{MaintainabilityDefnSelected2}:

@@

\subsection{Reusability \pmi{owner}}

\begin{defn} 
The degree to which a software module or other work product can be used in more
than one software system \citep{IEEEStdGlossarySET1990}. 
\end{defn}
\begin{defn}
Extent to which a program [or parts of a program] can be reused in other
applications - related to the packaging and scope of the functions that the
program performs \citep{pressman2005software}.
\end{defn}
\begin{defn} \label{ReusabilityDefnSelected}
The extent to which a software component can be used with or without adaptation
in a problem solution other than the one for which it was originally developed
\citep{kalagiakos2003non}.
\end{defn}
\begin{defn}
Reusability is the likelihood a segment of source code that can be used again to
add new functionalities with slight or no modification \citep{sandhu2010survey}.
\end{defn}

\noindent \textbf{Proposed Definition}

Definition \ref{ReusabilityDefnSelected}:

@@

\subsection{Portability \pmi{owner}}
\begin{defn}
The ease with which a system or component can be transferred from one hardware
or software environment to another \citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
An application is portable across a class of environments to the degree that the
effort required to transport and adapt it to a new environment in the class is
less than the effort of redevelopment \citep{mooney1990strategies}.
\end{defn}
\begin{defn} \label{PortabilityDefnSelected}
Effort required to transfer the program from one hardware and/or software system
environment to another \citep{pressman2005software}.
\end{defn}
\begin{defn}
A set of attributes that bear on the ability of software to be transferred from
one environment to another (including the organizational, hardware, of software
environment)\citep{pfleeger2006software}.
\end{defn}
\begin{defn}
Code possesses the characteristic of portability to the extent that it can be
operated easily and well on computer configurations other than its current
one. This implies that special function features, not easily available at other
facilities, are not used, that standard library functions and subroutines are
selected for universal applicability, and so on \citep{boehm2007software}.
\end{defn}
\begin{defn}
Portability refers to the ability to run a system on different hardware
platforms \citep{ghezzi1991fundamentals}.
\end{defn}

\noindent \textbf{Proposed Definition}

Definition \ref{PortabilityDefnSelected} rephrased:

@@

\subsection{Understandability \jc{owner}}

@@

\noindent \textbf{Proposed Definition}

\wss{Still needs to be completed}

\subsection{Interoperability \ad{owner}}

@@

\noindent \textbf{Proposed Definition}

Definition \ref{InteroperabilitySelected}
rephrased: Interoperability is the ability of different information systems,
devices and applications (‘systems’) to access, exchange, integrate and
cooperatively use data in a coordinated manner, within and across
organizational, regional and national boundaries, to provide timely and seamless
portability of information.

\wss{I moved the proposed definition to the end, to match the other sections.
  Hopefully I did not change the meaning.}

\subsection{Visibility/Transparency \ad{owner}}

@@

\noindent \textbf{Proposed definition}

Definition \ref{VisibilitySelected}.

\subsection{Reproducibility \wss{owner}}

@@

\noindent \textbf{Proposed definition}

\wss{Needs to be completed}

\subsection{Productivity \ad{owner}}

\begin{defn}
The best definition of the productivity of a process is
\[\text{Productivity} = \dfrac{\text{Outputs produced by the
process}}{\text{Inputs consumed by the process}}\]
Defining inputs. For the software process, providing a meaningful definition of
inputs is a nontrivial but generally workable problem. Inputs to the software
process generally comprise labor, computers, supplies, and other support
facilities and equipment. Defining outputs. The big problem in defining software
productivity is defining outputs. Here we find a defining delivered source
instructions (DSI) or lines of code as the output of the software process is
totally inadequate, and they argue that there are a number of deficiencies in
using DSI. However, most organizations doing practical productivity measurement
still use DSI as their primary metric \citep{Boehm1987}.
\end{defn}
\begin{defn}
\label{ProductivitySelected}
Productivity is the amount of output (what is produced) per unit of input
used.If we can measure the size of the software product and the effort required
to develop the product, we have:
\begin{align}
\text{productivity} = \text{size}/\text{effort}
\end{align}
Equation (1) assumes that size is the output of the software production process
and effort is the input to the process. This can be contrasted with the
viewpoint of software cost models where we use size as an independent variable
(i.e., an input) to predict effort which is treated as an output. Equation (1)
is simple to operationalize if we have a single dominant size measure, for
example, product size measured in lines of code \citep{Kitchenham2004}.
\end{defn}

\noindent \textbf{Proposed definition}

The first sentence of Definition \ref{ProductivitySelected}: Productivity is the
amount of output (what is produced) per unit of input used.

\subsection{Sustainability \wss{owner}}

@@

\noindent \textbf{Proposed definition}

\wss{Needs to be completed}

@@

\subsection{Completeness \ad{owner}}

@@

\noindent \textbf{Proposed definition}

The first sentence of Definition \ref{CompletenessSelected}: A specification is
complete to the extent that all of its parts are present and each part is fully
developed.

\subsection{Consistency \ad{owner}}

@@

\noindent \textbf{Proposed definition}

Definition \ref{ConsistencySelected}.

\subsection{Modifiability \jc{owner}}

@@

\subsection{Traceability \jc{owner}}

@@

\noindent \textbf{Proposed definition}

\wss{Needs to be completed.}

\subsection{Unambiguity \wss{owner}}

@@

\noindent \textbf{Proposed definition}

\wss{Needs to be completed.}

\subsection{Verifiability \wss{owner}}

@@

\noindent \textbf{Proposed definition}

\wss{Needs to be completed}

\subsection{Abstract \wss{owner}}
